Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-28 paper/current/main.tex
minor edit

Data, analysis, and associated code have been made publicly available and can be found at \url{https://github.com/murrayds/sci-mobility-emb}

@@

%% Word2vec parameters and training procedure
We used  \texttt{gensim} python implementation of the \textit{word2vec} model. The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between organizations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories,  6,580 organizations (76 \%) unique organizations are kept in the result embedding .
We set $\alpha$ as the default value of 0.025 and iterate five times over all training affiliation trajectories.

@@

We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data.
For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
Following past studies~\autocite{simini2012universal}, parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression \autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}

>>>>

Data, analysis, and associated code have been made publicly available and can be found at \url{https://github.com/murrayds/sci-mobility-emb}.

@@

%% Word2vec parameters and training procedure
We used  \texttt{gensim} python implementation of the \textit{word2vec} model. The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between organizations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories,  6,580 unique organizations are kept in the result embedding .
We set $\alpha$ as the default value of 0.025 and iterate five times over all training affiliation trajectories.

@@

We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data.
For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
Following past studies~\autocite{simini2012universal}, parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression \autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity, simini2012universal}
